Predicting the PCG Pseudo-Random Number Generator In Practice

### 2020-06-01 article/main.tex
Abstract

\newcommand{\todo}[1]{\textcolor{red}{TODO:[#1]}}

\title[Predicting the PCG Pseudo-Random Number Generator in Practice]{Predicting the (non-cryptographic) PCG Pseudo-Random Number Generator In Practice}

\author{Charles Bouillaguet\inst{1} \and Julia Sauvage\inst{2} \and Florette Martinez\inst{3}}

@@

\begin{abstract}
  \todo{blabla}
\end{abstract}

>>>>

%\newcommand{\todo}[1]{\textcolor{red}{TODO:[#1]}}

\title{Predicting the PCG Pseudo-Random Number Generator In Practice}

\author{Charles Bouillaguet\inst{1} \and Florette Martinez\inst{3} \and Julia Sauvage\inst{2}}

@@

\begin{abstract}
  The Permuted Congruential Generators (\textsf{PCG}) are popular conventional
  (non-cryptographic) pseudo-random generators designed in 2014. They are used
  by default in the \texttt{NumPy} scientific computing package. Even though
  they are not of cryptographic strength, their designer stated that predicting
  their output should be nevertheless be "challenging".

  In this article, we present a practical algorithm that recovers all the hidden
  parameters and reconstructs the successive internal states of the
  generator. This enables us to predict the next ``random'' numbers, and output
  the seeds of the generator. We have successfully executed the reconstruction
  algorithm using 512 bytes of challenge input; in the worst case, the process
  takes 20 000 CPU hours.

  This reconstruction algorithm makes use of cryptanalytic techniques, both
  symmetric and lattice-based. In particular, the most computationally expensive
  part is a guess-and-determine procedure that solves about $2^{52}$ instances
  of the \textsc{Closest Vector Problem} on a very small lattice.
\end{abstract}
